---
title: "Yukon River Fall Chum Salmon Inseason Mixed Stock Analysis"
output:
#  html_document:
#    toc: true
#    theme: united
  word_document:
    reference_docx: defalult-style_01.docx
    toc: false
#    highlight: zenburn
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_file = paste0(
        xfun::sans_ext(input), '-', Sys.Date(), '.docx'
      ),
      envir = globalenv()
    )
  })
---


```{r get_data, message=FALSE,echo=FALSE,error=FALSE,warning=FALSE}
#-------------------------------------------------------------------------------
# Setup file directories 
#-------------------------------------------------------------------------------
# Clear up existing files 
rm(list = ls(all.names = TRUE))
#-------------------------------------------------------------------------------
# Standard 
#-------------------------------------------------------------------------------
# Main <- 'C:/Projects/Yukon_River/Fall_Chum/MSA/' 
# fdr <- paste0(Main, 'R_functions/')  # R functions
#-------------------------------------------------------------------------------
# R projects 
#-------------------------------------------------------------------------------
fdr <- './R_functions'
#===============================================================================
#  1.0: Set Environment 
#===============================================================================
inSeason <- TRUE 
# Set year 
this.year <- 2023
# Inseason Data directory and file name 
wd_Ins <- './data/Inseason'
strata_file_Ins <- 'MSA_Strata_ins.csv'
# Stock Prop info file name 
stock_prop_file_Ins <- 'MSA_prop_ins.csv'  
# Inseasopn Pilot Data 
Pilot_Run_Ins <- 'Daily Passage By Species.csv'
# Pilot Station Var  
Pilot_Var_Ins <- 'Daily Variance By Species.csv'
#-------------------------------------------------------------------------------
#  1.1: Set MSA data directory and file names 
#-------------------------------------------------------------------------------
source(file.path(fdr,'Yukon_Chum_MSA_STD.R'))  
# Standard Output Stock figures 
ststockID <- c(4,7,8,10,11,19)
#	4 (P) Lower 
#	7 (P) UppKoy+Main
#	8 (P) Tanana Summer
#	10 (P) Tanana Fall  
#	11 (P) Border US
#	19 Total Canada (2004-present)
# ststocks needed to read as character
ststocks <- as.character(ststockID)
# Standard break date 
# '05/01','06/22','06/29','07/10','07/19','07/28','08/06','08/15','08/25','09/15'
stbreak <- stb(this.year)
# Pilot 

Pilot.total <- mlist[mlist$Strata==100,]
Pilot.summer <-mlist[mlist$Strata==101,]
Pilot.fall <- mlist[mlist$Strata==102,]
Pilot.fallinfall <- mlist[mlist$Strata==108,]

# Set legend name and order 
lgnames <- data.frame(t(stockID$GroupName))
names(lgnames) <- stockID$grpID
#-------------------------------------------------------------------------------
#  1.1: Set MSA data directory and file names 
#-------------------------------------------------------------------------------
#===============================================================================
#  2.0: Read summary data
#===============================================================================
#-------------------------------------------------------------------------------
#  2.1: Read Summer vs. Fall % data
#-------------------------------------------------------------------------------
# Read MSA minimum and max of the last year 
Pilot.d.min.max <- read.csv(file.path(wd_Sum,paste0(wd_Sum,'Pilot_d_min_max_',this.year-1,'.csv')),stringsAsFactors = FALSE)
# Read MSA Summer vs. Fall last year
Pilot.hsft <- read.csv(file.path(wd_Sum,'Pilot_sft.csv'),stringsAsFactors = FALSE)
# Find the number of years in the data 
years <- unique(Pilot.hsft$Year)
years <- years[order(years)]
# number of years
ny <- length(years)

############################################################################
#  Add kniter and rmarkdown libraries
############################################################################
library(knitr)
library(rmarkdown)
 add_legend <- function(...) {
   par(mar = c(0,0,4,0))
   plot(0, 0, type='n', bty='n', xaxt='n', yaxt='n',xlab='',ylab='')
   legend(...)
  }
```

```{r,fig.width=9, fig.height = 5,echo=FALSE,dpi=400}
#-------------------------------------------------------------------------------
#  Plot Pilot Station Passage and the strata break 
#-------------------------------------------------------------------------------
par(mfrow=c(1,1),mar = c(2,2,2,2),oma = c(3,3,3,3),yaxs='i',bty='l',las=1)
  rstr.y <- rstr[rstr$Year==this.year,]
  xlims<-c(min(stbreak),max(stbreak))
  plot(Run~Date, type='h',lwd=4,col='gray',data=Pilot,xlim=xlims,xaxt='n')
  axis.Date(1, at = stbreak,format= "%b%d",cex=0.6)
  abline(v=c(rstr.y$Strata_Start_Date),col=4,lwd=2)
  abline(v=max(rstr.y$Strata_End_Date),col=2,lwd=2)
mtext(paste("Sampling Strata"), side = 3, line = 0, outer = TRUE,cex=1.5)
mtext('Number of Salmon', side = 2, line = 1.5, las=0, outer = TRUE,cex=1.5)
mtext("Date", side = 1, line = 1, outer = TRUE,cex=1.5)
```
Figure 1.  Daily sonar counts attributed to chum salmon (bars) showing genetic sampling time frames (droplines), project operated near Pilot Station, Yukon Area, `r this.year`.

```{r,fig.width=9, fig.height = 5,echo=FALSE,dpi=400}
#-------------------------------------------------------------------------------
#  Plot mean stock proportion by sampling strata 
#-------------------------------------------------------------------------------
# Pilot Station timing 
Pilot.stp <- Pilot.m[,c('Year','Strata','Run', ststocks)]
Pilot.stp[,ststocks] <- 100*Pilot.stp[,ststocks] /Pilot.stp$Run
Pilot.stpl <- melt(Pilot.stp[,c('Year','Strata',ststocks)], 
                   id.vars = c('Year','Strata'), variable.name = "group", value.name = "percent") 
Pilot.stpl <- Pilot.stpl[order(Pilot.stpl$Year,Pilot.stpl$Strata),]
gname <- stockID[stockID$grpID %in%ststockID,c('GroupName')]      
names(gname) <- ststockID
# Base plot 
#layout(matrix(1:2, ncol=2), widths=c(3,1))
par(mar=c(4, 4, 4, 0),yaxs='i',bty='l',las=1) 
temp1 <- Pilot.stpl[Pilot.stpl$group==ststockID[1],]
plot(order(temp1$Strata),type='n', xlim=c(1,7),ylim=c(0,100), ylab='Stock Percent',xlab='Sample Strata Number')
for (i in 1:6){
  lines(percent~Strata, type ='o',lwd=2,col=i,pch=i,data=Pilot.stpl[Pilot.stpl$group==ststockID[i],])
}
title(main = this.year)
legend('topright',legend = gname,col = c(1:6), pch=c(1:6),lty=1,lwd=2,bty = 'n')
mtext('Stock Percent', side = 2, line = 1,las=0, outer = TRUE)
mtext("Sampling Strata", side = 1, line = 1, outer = TRUE)

```
Figure 2.  Mean proportion of chum salmon stock groups by sampling strata, Yukon Area, `r this.year`.

```{r,fig.width=9, fig.height = 5,echo=FALSE,dpi=400}
#-------------------------------------------------------------------------------
#  Plot passage by stock and strata 
#-------------------------------------------------------------------------------
Pilot.stn <- Pilot.m[,c('Year','Strata','Run', c('4','7','8','11','19','10'))]
gname <- lgnames[c('4','7','8','11','19','10')]      

par(mfrow=c(1,1),mar=c(4.1, 6.1, 4.1, 4.1),yaxs='i',bty='l',las=1) 
barplot(t(Pilot.stn[,-c(1:3)]),beside=TRUE,col=c(8,2:6),
      names.arg = rstr[which(rstr$Year==this.year), 'Time_Frames']
        )
title(main = this.year)
legend('topright',legend = gname, fill = c(8,2:6),bty = 'n')
mtext('Run size', side = 2, line = 4,las=0)
mtext("Sampling Strata", side = 1, line = 2)
```
Figure 2.5  Mean proportion of chum salmon stock groups by sampling strata, Yukon Area, `r this.year`.


```{r,fig.width=9, fig.height = 5,echo=FALSE,dpi=400}
#-------------------------------------------------------------------------------
#  Plot stock proportion by Standard Strata
#-------------------------------------------------------------------------------
gname <- stockID[stockID$grpID %in%ststockID,c('GroupName')]      
names(gname) <- ststockID
#layout(matrix(1:2, ncol=2), widths=c(3,1))
par(mar = c(4,4,4,0),yaxs='i',bty='l',las=1)
temp1 <- with(Pilot.d.min.max, Pilot.d.min.max[group ==ststockID[1],])
plot(order(temp1$stbreak),type='n', xlim=c(1,9),ylim=c(0,100), ylab='',xlab='',
     yaxt='n',xaxt='n')
axis(2, seq(0,100,20),las=2, font=2 )
axis(1, seq(1,9,1), labels = stbl,tick=1)
for(i in 1:6){
  temp <- with(Pilot.d.min.max, Pilot.d.min.max[group ==ststockID[i],])  
  temp <- temp[order(temp$stbreak),]
  with(temp, lines(stbreak,Mean, type='o',lwd=2,col=i,pch=i))
}
txt <- c(gname)
legend('topright',legend=txt,col=c(1:6),pch=c(1:6),lty=1,lwd=2,bty='n')
mtext(paste(" "), side = 3, line = 0, outer = TRUE)
mtext('Stock Percent', side = 2, line = 1,las=0, outer = TRUE)
mtext("Dates", side = 1, line = 1, outer = TRUE)

```
Figure 3.  Mean proportion of chum salmon stock groups by standard sampling strata, Yukon Area, 2004-`r this.year-1`.
```{r,fig.width=9, fig.height = 9,echo=FALSE,dpi=400}
#-------------------------------------------------------------------------------
#  Plot mean stock prop overlapped by historical min-max
#-------------------------------------------------------------------------------
par(mfrow=c(4,2),mar = c(2,2,2,2),oma = c(3,3,3,3),yaxs='i',bty='l')
fig.stock.id <- c(4,7,8,10,11,19,16,3)
n <- length(fig.stock.id)
for(j in 1:n){
  temp1 <- with(Pilot.d.min.max, Pilot.d.min.max[group ==fig.stock.id[j],])
  temp1 <- temp1[order(temp1$stbreak),]
  plot(Mean~stbreak,data=temp1, type='n',xlim=c(1,9),ylim=c(0,100), 
       yaxt='n',xaxt='n',main=unique(temp1$GroupName))
  axis(2, seq(0,100,20),las=2, label=FALSE)
  if(j %in% c(1,3,5,7)) {axis(2, seq(0,100,20),las=2, font=2)}
  axis(1,seq(1,9,1), labels = FALSE,tick=1)
  if(j %in% c(7:8)) {axis(1, seq(1,9,1), labels = stbl,tick=1)}
  with(temp1,polygon(c(stbreak,rev(stbreak)),c(Min,rev(Max)),col=tcol('gray',0),border=NA))
  lines(percent~stbreak,lwd=2,col=2, data=Pilot.sd[Pilot.sd$ group ==fig.stock.id[j],])
  }
mtext(paste("Stock Proportion thru Run"), side = 3, line = 0, outer = TRUE)
mtext('Stock Percent', side = 2, line = 1, outer = TRUE)
mtext("Dates", side = 1, line = 1, outer = TRUE)

```
Figure 4.  Minimum and maximum (2004-`r this.year-1`) and `r this.year` mean stock proportion by standard sampling strata, comparing the major chum salmon components, Yukon Area.
```{r,fig.width=9, fig.height = 9,echo=FALSE,dpi=400}
#-------------------------------------------------------------------------------
# Plot Summer vs. Fall cross over all years and strata
#-------------------------------------------------------------------------------
  par(mfrow=c(5,5),mar = c(2,2,2,2),oma = c(3,3,3,3),yaxs='i',bty='l') 
# yax: Index determining vertical axis needs to be labeled 
  yax <- c(1,which(1:(ny+1)%%5==0)+1) 
# sax: Index determining horizontal axis needs to be labeled  
  xax <- ny-(ny+1)%%5
  for(i in 1:ny){
    temp <- with(Pilot.hsft, Pilot.hsft[Year==years[i],])
    plot(Summer~stbreak, type ='o',col=4, xlim=c(1,9),ylim=c(0,100), 
         yaxt='n',xaxt='n',lwd = 2, data=temp,main=years[i])
    lines(Fall~stbreak,type ='o',col=2,lwd = 2, data=temp)
    axis(2, seq(0,100,20),las=2, labels=NA)
    if (i %in% yax) axis(2, seq(0,100,20),las=2, font=2)
    axis(1, seq(1,9,1),labels = NA,cex.axis = 0.9)
    if (i > xax) axis(1, seq(1,9,1), labels = stbl,cex.axis = 0.9)
  }
# This year 
 plot(Summer~stbreak, type ='o',col=4, xlim=c(1,9),ylim=c(0,100), 
     yaxt='n',xaxt='n',lwd = 2, data=Pilot.sft,main=this.year)
 lines(Fall~stbreak,type ='o',col=2,lwd = 2, data=Pilot.sft)
# axis(2, seq(0,100,20),las=2, font=2)
 axis(1, seq(1,9,1), labels = stbl,cex.axis = 0.9)
 
  mtext(paste("Summer vs. Fall (All Strata)"), side = 3, line = 0, outer = TRUE,cex=1.5)
  mtext('Stock Percent', side = 2, line = 1, outer = TRUE,cex=1.5)
  mtext("Dates ", side = 1, line = 1, outer = TRUE,cex=1.5)
```
Figure 5.  Crossover of summer and fall chum salmon based on genetic stock analysis (standard sampling strata), Yukon Area, 1999-2002 using allozymes and 2004-`r this.year` using microsatellites.
```{r,fig.width=9, fig.height = 9,echo=FALSE,dpi=400}
#-------------------------------------------------------------------------------
# Plot Summer vs. Fall cross over all years and strata
#-------------------------------------------------------------------------------
 par(mfrow=c(5,5),mar = c(2,2,2,2),oma = c(3,3,3,3),yaxs='i',bty='l') 
    for(i in 1:ny){
    temp <- with(Pilot.hsft, Pilot.hsft[Year==years[i],])
    plot(Summer~stbreak, type ='o',col=4, xlim=c(4,6),ylim=c(0,100), 
         yaxt='n',xaxt='n',lwd = 2, data=temp,main=years[i])
    lines(Fall~stbreak,type ='o',col=2,lwd = 2, data=temp)
    axis(2, seq(0,100,20),las=2, labels=NA)
    if (i %in% yax) axis(2, seq(0,100,20),las=2, font=2)
    axis(1, seq(1,9,1),labels = NA,cex.axis = 0.9)
    if (i >xax) axis(1, seq(1,9,1), labels = stbl,cex.axis = 0.9)
    }
# This year 
  plot(Summer~stbreak, type ='o',col=4, xlim=c(4,6),ylim=c(0,100), 
       yaxt='n',xaxt='n',lwd = 2, data=Pilot.sft,main=this.year)
  lines(Fall~stbreak,type ='o',col=2,lwd = 2, data=Pilot.sft)
#  axis(2, seq(0,100,20),las=2, font=2)
  axis(1, seq(1,9,1), labels = stbl,cex.axis = 0.9)
  
  mtext(paste("Summer vs. Fall"), side = 3, line = 0, outer = TRUE,cex=1.5)
  mtext('Stock Percent', side = 2, line = 1, las=0, outer = TRUE,cex=1.5)
  mtext("Dates", side = 1, line = 1, outer = TRUE,cex=1.5)
```
Figure 6.  Crossover of summer and fall chum salmon (3 periods) based on genetic stock analysis (standard sampling strata), Yukon Area, 1999-2002 using allozymes and 2004-`r this.year` using microsatellites.
```{r,fig.width=9, fig.height = 9,echo=FALSE,dpi=400}
if(dim(Pilot.fall)[1]>0){
  temp <- Pilot.fall[Pilot.fall$grpID %in% c(4,7,8,10,11,13,16),]
temp$pct <- with(temp, paste0(round(100*p),'%'))
par(mfrow=c(1,1),mar = c(4,4,4,7),oma = c(3,3,3,3))
pie(temp$p, labels = paste(temp$GroupName,temp$pct),col=c(2:8),main="Stock Proportion (July 19 to End of Season)")
#par(new=TRUE)
#pie(temp$p,density=10, labels='',angle=c(20,90,30,10,40,0))
#pie(temp$p, labels = paste(temp$GroupName,temp$pct),col=gray.colors(6),main="Stock Proportion (July 19 to End of Season)")
}
```
Figure 7. Contributions of chum salmon based on genetic analysis during the fall season (July 19 to end of season), sampled at the mainstem sonar operated near Pilot Station, Yukon Area, `r this.year`.
```{r,fig.width=9, fig.height = 9,echo=FALSE,dpi=400}
if(dim(Pilot.fallinfall)[1]>0){
  temp <- Pilot.fallinfall[Pilot.fallinfall$grpID %in% c(10,11,19),]
temp$pct <- with(temp, paste0(round(100*p),'%'))
par(mfrow=c(1,1),mar = c(4,4,4,7),oma = c(3,3,3,3))
pie(temp$p, labels = paste(temp$GroupName,temp$pct),col=c(2:8),main="Stock Proportion (July 19 to End of Season)")
#par(new=TRUE)
#pie(temp$p,density=10, labels='',angle=c(20,90,30,10,40,0))
#pie(temp$p, labels = paste(temp$GroupName,temp$pct),col=gray.colors(6),main="Stock Proportion (July 19 to End of Season)")
}
```
Figure 8. Contributions of Fall chum salmon based on genetic analysis during the fall season (July 19 to end of season), sampled at the mainstem sonar operated near Pilot Station, Yukon Area, `r this.year`.