---
title: "Yukon River Fall Chum Salmon Postseason Mixed Stock Analysis"
date: '`r format(Sys.time(), "%d %B, %Y")`'
author: "Project Leads: Bonnie Borba (bonnie.borba@alaska.gov)"
output:
  html_document:
    df_print: paged
    fig_caption: true
    toc: true
    toc_depth: 2
    toc_float: true
#  word_document:
#    reference_docx: defalult-style_01.docx
#    toc: false
#    highlight: zenburn
#knit: (function(input, ...) {
#    rmarkdown::render(
#      input,
#      output_file = paste0(
#        xfun::sans_ext(input), '-', Sys.Date(), '.docx'
#      ),
#      envir = globalenv()
#    )
#  })
---
<style type="text/css">
.caption {
    font-size: large;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE, message = FALSE)
```



```{r get_data, message=FALSE,echo=FALSE,error=FALSE,warning=FALSE}
#-------------------------------------------------------------------------------
# Setup file directories 
#-------------------------------------------------------------------------------
# Clear up existing files 
rm(list = ls(all.names = TRUE))
library(ggplot2)    # Used for ggplot graphics 
library(reshape2)
library(lubridate)

okabe <- c("#E69F00","#56B4E9", "#009E73","#F0E442","#0072B2","#D55E00","#CC79A7" )
options(ggplot2.discrete.colour = okabe)
options(ggplot2.discrete.fill = list(okabe))
#-------------------------------------------------------------------------------
# R projects 
#-------------------------------------------------------------------------------
fdr <- './R_functions'
wd_Out <- './Output'
wd_MSA <- './data/MSA_data'
source(file.path(fdr,'ggplot_theme.r'))
theme_set(theme_simple())

#===============================================================================
#  1.0: Run MSA
#===============================================================================
postSeason <- TRUE 
#  Overwrite CI: Do this when you updated historical data. 
ciOverwrite <- FALSE
# Save output files 
filesave <- FALSE
# Set year 
this.year <- 2025

#'------------------------------------------------------------------------------
##  1.0 : Set MSA and Pilot data file names ---- 
#'------------------------------------------------------------------------------
# Strata info file name 
strata_file <- 'MSA_Strata.csv'
# Stock Prop info file name 
stock_prop_file <- 'MSA_prop.csv'
# Stock ID file name 
stock_id_file <- 'StockID.csv'
# Pilot Station Run  file
Pilot_Run <- 'Daily_Passage_By_Species_'
# Pilot Station Var  
Pilot_Var <- 'Daily_Variance_By_Species_'

#'------------------------------------------------------------------------------
#' Output file names 
#'------------------------------------------------------------------------------ 
# Output Summary EXCEL file name 
sumxlsx <- paste0('Yukon_Pilot_Chum_MSA_',Sys.Date(),'.xlsx')
# Output JTC EXCEL file name 
jtcxlsx <- paste0('JTC_MSA_',Sys.Date(),'.xlsx')

# Output Annual Stock proportions by summer and fall:
sf_p <- paste0('Pilot_sfp_',this.year,'.csv')
# Output Annual Summer vs. Fall Stock proportions by standard break:
sf_t <- paste0('Pilot_sft_',this.year,'.csv')
# Output min_max file name 
min_max <- paste0('Pilot_d_min_max_',this.year,'.csv')


#-------------------------------------------------------------------------------
#  1.1: Set MSA data directory and file names 
#-------------------------------------------------------------------------------
# Run postseason data processing routines 
source(file.path(fdr,'Yukon_Chum_MSA_STD.R'))  
# Run postseason summary routines 
source(file.path(fdr,'Yukon_Fall_Chum_MSA_Post_Season.R'))  
# This will create 
# Summary EXCEL files,  EXCEL file for JTC output
# MSA prop and strata csv (data/MSA_data folder)



# Standard Output Stock figures 
ststockID <- c(4,7,8,10,11,19)
#	4 (P) Lower 
#	7 (P) UppKoy+Main
#	8 (P) Tanana Summer
#	10 (P) Tanana Fall  
#	11 (P) Border US
#	19 Total Canada (2004-present)
# ststocks needed to read as character
ststocks <- as.character(ststockID)
# Standard break date 
# '05/01','06/22','06/29','07/10','07/19','07/28','08/06','08/15','08/25','09/15'
stbreak <- stb(this.year)

Pilot.total <- mlist[mlist$Strata==100,]
Pilot.summer <-mlist[mlist$Strata==101,]
Pilot.fall <- mlist[mlist$Strata==102,]
Pilot.fallinfall <- mlist[mlist$Strata==108,]

# Set legend name and order 
lgnames <- data.frame(t(stockID$GroupName))
names(lgnames) <- stockID$grpID
#-------------------------------------------------------------------------------
#  1.1: Set MSA data directory and file names 
#-------------------------------------------------------------------------------
#===============================================================================
#  2.0: Read summary data
#===============================================================================
#-------------------------------------------------------------------------------
#  2.1: Read Summer vs. Fall % data
#-------------------------------------------------------------------------------
# Read MSA Strata data
Pilot.d.min.max <- read.csv(file.path(wd_Sum,paste0('Pilot_d_min_max_',this.year-1,'.csv')),stringsAsFactors = FALSE)
# Read MSA Strata data
Pilot.hsft <- read.csv(file.path(wd_Sum,paste0('Pilot_sft_',this.year-1,'.csv')),stringsAsFactors = FALSE)
# Find the number of years in the data 
years <- unique(Pilot$Year)
years <- years[order(years)]
# number of years
ny <- length(years)

############################################################################
#  Add kniter and rmarkdown libraries
############################################################################
library(knitr)
library(rmarkdown)
library(kableExtra)
 add_legend <- function(...) {
   par(mar = c(0,0,4,0))
   plot(0, 0, type='n', bty='n', xaxt='n', yaxt='n',xlab='',ylab='')
   legend(...)
  }
```

\newpage
# Pilot Station Passage 
```{r,fig.width=9, fig.height = 5,echo=FALSE,dpi=400}
# Pilot Station timing 
  rstr.y <- rstr[rstr$Year==this.year,]
  xlims<-c(min(stbreak),max(stbreak))  
p1 <-   ggplot() +
      geom_bar(data = Pilot[Pilot$Year==this.year,], aes(x=Date,y=Run), stat='identity',color='grey')+
      scale_x_date(expand=c(0, 2),limits=as.Date(xlims),oob=oob_keep,date_labels="%b%d")+
      scale_y_continuous(expand=expansion(mult = c(0, .25)), limits=c(0, NA))+
      geom_vline(xintercept = c(rstr.y$Strata_Start_Date),color=4) + 
      geom_vline(xintercept = max(rstr.y$Strata_End_Date,na.rm=TRUE),color=2)+
      labs(title="Pilot Station Sampling Strata",x="Date",y="Number of Salmon")
print(p1)
```
**Figure 1.  Daily sonar counts attributed to chum salmon (bars) showing genetic sampling time frames (droplines), project operated near Pilot Station, Yukon Area, `r this.year`.**

# Historical Pilot Station Passage 
```{r,fig.width=9, fig.height = 18,echo=FALSE,dpi=400}
# Pilot Station timing 
  Pilot$Date2 <- Pilot$Date
  year(Pilot$Date2) <- this.year
  inc <- median(with(Pilot,tapply(Run,Year,max))) 
ridge_data <- data.frame()
   for (i in 1:ny) {
    ridge <- Pilot[Pilot$Year==years[i],]
    ridge_data <- rbind(ridge_data, data.frame(
      x = ridge$Date2,
      y = ridge$Run + (i - 1) * inc,
      Year = years[i]
    ))
  }  
   maxy <- max(ridge_data$y)
   tick <- data.frame(x=min(ridge$Date2),y=(1:ny) * inc,label=years)
  p <- ggplot()+
    # Create polygons for each ridge
    geom_polygon(data=ridge_data, aes(x = x, y = y, fill = factor(Year)), color = NA, alpha = 0.3) +
    # Add horizontal dashed lines
    geom_hline(data = data.frame(y = (0:(ny-1)) * inc), aes(yintercept = y), 
               color = "grey", linetype = "solid", size = 0.25) +
    # Set axis labels and title
    labs(x = 'Date', y = NULL) +
    scale_fill_manual(values = rainbow(ny)) +
    geom_text(data=tick,aes(x=x,y=y-0.1*inc,label=label),size=5,vjust=1.0,hjust=1.0)+
     scale_y_continuous(expand=c(0,0),limits=c(0,NA))+
        theme(
#      axis.title = element_text(size = 14),
      axis.text.y = element_blank(),
#      axis.text.x = element_text(size=14),
     axis.line.y = element_blank(),
      axis.ticks.y = element_blank(),
      panel.grid = element_blank(),
      legend.position = "none",
#      plot.margin = margin(0, 0, 0, 0)  # No extra space
     ) 
  print(p)

```
**Figure 1.a.  Daily sonar counts attributed to chum salmon across all years, project operated near Pilot Station, Yukon Area.**


# Historical Pilot Station Passage 
```{r,fig.width=9, fig.height = 18,echo=FALSE,dpi=400}
# Pilot Station timing 
  pilot.dp <- merge(Pilot[,c('Year','Date','Run','Strata')], 
                   Pilot.mp[,c('Year','Strata',c('4','7','8','11','19','10'))],by=c('Year','Strata'))
gname <- lgnames[c('4','7','8','11','19','10')] 
  pilot.dp[,-c(1:4)] <- pilot.dp[,-c(1:4)]*pilot.dp$Run
  pilot.dp <- pilot.dp[order(pilot.dp$Year,pilot.dp$Date),]
  pilot.dp$Date2 <- pilot.dp$Date
  year(pilot.dp$Date2) <- this.year
  rstr.y <- rstr[rstr$Year==this.year,]

for(j in 1:6){
  temp <- pilot.dp[,c(1,11,4+j)]
  names(temp) <- c('Year','Date','Run')
  temp$Run[is.na(temp$Run)]<- 0
  inc <- median(tapply(temp$Run,temp$Year,max,na.rm=TRUE),na.rm=TRUE)  
  ry <-c(0,inc*ny)  
  for (i in 1:ny) {
    temp[temp$Year==years[i],'Run'] <- temp[temp$Year==years[i],'Run']+(i - 1) * inc
  }  
   maxy <- max(temp$Run)
   tick <- data.frame(x=min(pilot.dp$Date2),y=(1:ny) * inc,label=years)  
  p <- ggplot()+
    # Create polygons for each ridge
    geom_line(data=temp, aes(x = Date, y = Run, fill = factor(Year)),color=j)+
    # Add horizontal dashed lines
    geom_hline(data = data.frame(y = (0:(ny-1)) * inc), aes(yintercept = y), 
               color = "grey", linetype = "solid", size = 0.25) +
    # Set axis labels and title
    labs(title=paste("Stock:",gname[j]),x = 'Date', y = NULL) +
    scale_fill_manual(values = rainbow(ny)) +
    geom_text(data=tick,aes(x=x,y=y-0.1*inc,label=label),size=5,vjust=1.0,hjust=0)+
     scale_y_continuous(expand=c(0,0),limits=c(0,NA))+
        theme(
#      axis.title = element_text(size = 14),
      axis.text.y = element_blank(),
#      axis.text.x = element_text(size=14),
     axis.line.y = element_blank(),
     axis.ticks.y = element_blank(),
      panel.grid = element_blank(),
      legend.position = "none",
#      plot.margin = margin(0, 0, 0, 0)  # No extra space
     ) 
  print(p)
   } 
```
**Figure 1.a.  Daily sonar counts attributed to chum salmon across all years, project operated near Pilot Station, Yukon Area.**



# Stock proportion by sampling strata
```{r,fig.width=9, fig.height = 5,echo=FALSE,dpi=400}
#-------------------------------------------------------------------------------
#  Plot mean stock proportion by sampling strata 
#-------------------------------------------------------------------------------
# Pilot Station timing 
Pilot.stp <- Pilot.m[Pilot.m$Year == this.year,c('Year','Strata','Run', ststocks)]
Pilot.stp[,ststocks] <- 100*Pilot.stp[,ststocks] /Pilot.stp$Run
Pilot.stpl <- melt(Pilot.stp[,c('Year','Strata',ststocks)], 
                   id.vars = c('Year','Strata'), variable.name = "group", value.name = "percent") 
Pilot.stpl <- Pilot.stpl[order(Pilot.stpl$Year,Pilot.stpl$Strata),]
gname <- stockID[stockID$grpID %in%ststockID,c('GroupName')]      
names(gname) <- ststockID

p1 <-   ggplot(data = Pilot.stpl, aes(x=Strata,y=percent,group=group))+
        geom_line(aes(colour=group))+geom_point(aes(shape=group,color=group))+ 
        scale_color_manual(values = c(1:6),labels = gname)+scale_shape_manual(values = c(1:6),labels = gname)+
        labs(x='Sampling Strata',y='Stock Percent')+
        scale_x_continuous(expand=expansion(add = c(.25, .25)),breaks=seq(1,10), limits=c(1, NA))
  print(p1)

```
**Figure 2.  Mean proportion of chum salmon stock groups by sampling strata, Yukon Area, `r this.year`.**

\newpage

##  Stock proportion by strata (bar graph) 
```{r,fig.width=9, fig.height = 5,echo=FALSE,dpi=400}
Pilot.stn <- Pilot.m[Pilot.m$Year == this.year,c('Year','Strata', c('4','7','8','11','19','10'))]
Pilot.stnl <- melt(Pilot.stn, 
                   id.vars = c('Year','Strata'), variable.name = "group", value.name = "n")
gname <- lgnames[c('4','7','8','11','19','10')]      

p1 <-   ggplot(data=Pilot.stnl,aes(x=as.factor(Strata),y=n,group=group))+ 
        geom_bar(stat = "identity", position = "dodge",aes(fill=group))+
        labs(x = "Sampling Strata", y = "Run size")+
        scale_fill_manual(values = c(1:6),labels = gname)
print(p1)
```
**Figure 2.5  Mean proportion of chum salmon stock groups by sampling strata, Yukon Area, `r this.year`.**


# Historical mean stock proportion  

```{r,fig.width=9, fig.height = 5,echo=FALSE,dpi=400}
#-------------------------------------------------------------------------------
#  Plot mean stock proportion by Standard Strata
#-------------------------------------------------------------------------------
gname <- stockID[stockID$grpID %in%ststockID,c('GroupName')]      
names(gname) <- ststockID
df <- Pilot.d.min.max[Pilot.d.min.max$group %in% ststockID,]
df$group <- as.factor(df$group)
p1 <- ggplot(data = df, aes(x=as.factor(stbreak),y=Mean,group=group))+
      geom_line(aes(colour=group))+geom_point(aes(shape=group,colour=group))+                           scale_colour_manual(values = c(1:6),labels = gname)+scale_shape_manual(values = c(1:6),labels = gname)+
        scale_x_discrete(labels=stbl)+labs(x='Dates',y='Stock Percent')
  print(p1)

```
**Figure 3.  Mean proportion of chum salmon stock groups by standard sampling strata, Yukon Area, 2004-`r this.year-1`.**

\newpage
# Standard Stock Proportion 
```{r,fig.width=9, fig.height = 9,echo=FALSE,dpi=400}
fig.stock.id <- c(4,7,8,10,11,19,16,3)
gname <- stockID[stockID$grpID %in%fig.stock.id,c('GroupName','grpID')]
gname$grpID <- as.character(gname$grpID)
new_order_indices <- match(as.character(fig.stock.id), gname$grpID)
name <- gname[new_order_indices,'GroupName']
df <- Pilot.d.min.max[Pilot.d.min.max$group %in% fig.stock.id,]
plt <- Pilot.sd[(Pilot.sd$group %in% fig.stock.id)&(Pilot.sd$Year==this.year),]
plt$group <- as.numeric(as.character(plt$group))
ggplot()+
  geom_ribbon(data=df,aes(x=(stbreak),ymin = Min, ymax = Max), fill = "gray", alpha = 0.5) +
  geom_line(data=plt,aes(x=stbreak, y=percent),colour=2)+
  scale_x_continuous(expand=expansion(add = c(.25, .25)),breaks=seq(1,10), limits=c(1, NA))+
  facet_wrap( ~factor(group,labels=name,levels=as.character(fig.stock.id)),axes='all',axis.labels='margins',ncol=2)+
  labs(title="Stock Proportion thru Run",x="Dates",y='Stock Percent')

```
**Figure 4.  Minimum and maximum (2004-`r this.year-1`) and `r this.year` mean stock proportion by standard sampling strata, comparing the major chum salmon components, Yukon Area.**

\newpage
# Summer vs. Fall:  All seasons
```{r,echo=FALSE}
# Summer vs. Fall data preparation:Postseatson
#   df<- melt(Pilot.sft[,c(1,2,4,5)],id.vars=c('Year','stbreak'), 
#                       variable.name='SF', value.name='percent')
   df<- reshape(Pilot.sft[,c(1,2,4,5)], idvar =c('Year','stbreak'),
                varying =3:4,
                v.names = 'percent',
                timevar='SF',
                times=names(Pilot.sft[,c(1,2,4,5)])[3:4],
                direction = 'long'
                )
```

```{r,fig.width=9, fig.height = 9,echo=FALSE,dpi=400}
#-------------------------------------------------------------------------------
# Plot Summer vs. Fall cross over all years and strata
#-------------------------------------------------------------------------------
  ggplot(data=df,aes(x=as.factor(stbreak),y=percent,group=SF)) + theme_simple() + 
      geom_line(aes(color=SF ))+
      geom_point(aes(color=SF),size=2)+
      facet_wrap( ~Year,axes='all',axis.labels='margins',ncol=5) +
      scale_x_discrete(labels=stbl,guide = guide_axis(check.overlap = TRUE)) + 
	  ylim(0, 100)+
      theme(axis.text.x = element_text(size=7))+
      labs(title = "Summer vs. Fall (All Strata)",x="Dates")

```
**Figure 5.  Crossover of summer and fall chum salmon based on genetic stock analysis (standard sampling strata), Yukon Area, 1999-2002 using allozymes and 2004-`r this.year` using microsatellites.**

## Summer vs. Fall:  During the transition periods
```{r,fig.width=9, fig.height = 9,echo=FALSE,dpi=400}
 ggplot(data=df,aes(x=as.factor(stbreak),y=percent,group=SF))+ 
      geom_line(aes(color=SF ))+
      geom_point(aes(color=SF),size=2)+
      facet_wrap( ~Year,axes='all',axis.labels='margins',ncol=5) +
      scale_x_discrete(labels=stbl,limit=factor(4:6),guide = guide_axis(check.overlap = TRUE)) + 
	  ylim(0, 100)+
      theme(axis.text.x = element_text(size=7))+
      labs(title = "Summer vs. Fall",x="Dates")

```
**Figure 6.  Crossover of summer and fall chum salmon (3 periods) based on genetic stock analysis (standard sampling strata), Yukon Area, 1999-2002 using allozymes and 2004-`r this.year` using microsatellites.**

```{r,fig.width=9, fig.height = 9,echo=FALSE,dpi=400}


```
**Figure 7. Contributions of chum salmon based on genetic analysis during the fall season (July 19 to end of season), sampled at the mainstem sonar operated near Pilot Station, Yukon Area, `r this.year`.**
```{r,fig.width=9, fig.height = 9,echo=FALSE,dpi=400}

  temp <- Pilot.fallinfall[Pilot.fallinfall$grpID %in% c(10,11,19),]
temp$pct <- with(temp, paste0(round(100*p),'%'))
ggplot(temp,aes(x='',y=pct,fill=GroupName))+
#geom_bar(stat = "identity", color = "white") +  
geom_col(color='black')+
geom_text(aes(x=1.6, label=pct),position=position_stack(vjust=0.5))+
coord_polar("y")+
labs(title="Stock Proportion (July 19 to End of Season)",x='',y='')+
  theme(axis.line = element_blank(),
       axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        panel.grid = element_blank())

```
**Figure 8. Contributions of Fall chum salmon based on genetic analysis during the fall season (July 19 to end of season), sampled at the mainstem sonar operated near Pilot Station, Yukon Area, `r this.year`.**


```{r,echo=FALSE}
table <- mlist[which(mlist$Strata<10 & mlist$SortID<20),]
```

\newpage
# Tables
**Table 1. Genetic proportions of chum salmon stock groupings from samples collected from mainstem Yukon River (Pilot Station) sonar test fishery `r this.year`.**

```{r,echo=FALSE}
table$p <- table$p*100
Prop <- dcast(table,SortID+GroupName~Strata,value.var='p')
s.names <- with(rstr.y,paste(paste('Strata',Strata),Time_Frames,paste('n=',Sample_Size),sep='<br/>'))
t.names <-c('Stock',s.names)
kable(Prop[,-1],digits=1,caption=paste("Genetic Proportions of chum salmon stock grouping used to converst Pilot Station passage estimates to numbers of fish","this.year"),format = "html",col.names=t.names,format.args = list(big.mark = ",",scientific = F),escape=FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

\newpage
**Table 2. Genetic estimates of chum salmon passage by stock groups applied to mainstem Yukon River (Pilot Station) sonar counts `r this.year`.**

```{r,echo=FALSE}
n <- dcast(table,SortID+GroupName~Strata,value.var='mean')
total <- rowSums(n[,-c(1,2)])
n <- cbind(n,total)
s.names <- with(rstr.y,paste(paste('Strata',Strata),Time_Frames,paste('n=',Sample_Size),sep='<br/>'))
t.names <-c('Stock',s.names,'Total')
kable(n[,-1],digits=0,format = "html", booktabs = T,longtable=T,col.names=t.names,format.args = list(big.mark = ",",scientific = F),escape=FALSE) %>%
  kable_styling(bootstrap_options = c("striped"))
```

