---
title: "Yukon River Fall Chum Salmon Inseason Mixed Stock Analysis"
date: '`r format(Sys.time(), "%d %B, %Y")`'
author:
- name: "Project Leads: Bonnie Borba (bonnie.borba@alaska.gov)"
  affiliation: "Alaska Department of Fish and Game, Division of Commercial Fisheries" 
- name: "Samples analyzed by Conservation Genetics Laboratory"
  affiliation: "U.S. Fish and Wildlife Service"
output:
  html_document:
    df_print: paged
#    fig_caption: false
#    toc: true
#    toc_depth: 2
#    toc_float: true
#    theme: united
#  word_document:
#    reference_docx: defalult-style_01.docx
#    toc: false
#    highlight: zenburn
#knit: (function(input, ...) {
#    rmarkdown::render(
#      input,
#      output_file = paste0(
#        xfun::sans_ext(input), '-', Sys.Date(), '.docx'
#      ),
#      output_dir = file.path('./Output'),
#      envir = globalenv()
#    )
#  })
---


```{r get_data, message=FALSE,echo=FALSE,error=FALSE,warning=FALSE}
#-------------------------------------------------------------------------------
# Setup file directories 
#-------------------------------------------------------------------------------
# Clear up existing files 
rm(list = ls(all.names = TRUE))
#-------------------------------------------------------------------------------
# Standard 
#-------------------------------------------------------------------------------
# Main <- 'C:/Projects/Yukon_River/Fall_Chum/MSA/' 
# fdr <- paste0(Main, 'R_functions/')  # R functions
#-------------------------------------------------------------------------------
# R projects 
#-------------------------------------------------------------------------------
fdr <- './R_functions'
#===============================================================================
#  1.0: Set Environment 
#===============================================================================
inSeason <- TRUE 
# Set year 
this.year <- 2025
# Inseason Data directory and file name 
wd_Ins <- './data/Inseason'
wd_Sums <- './data/Summary_data'
strata_file_Ins <- 'MSA_Strata_ins.csv'
# Stock Prop info file name 
stock_prop_file_Ins <- 'MSA_prop_ins.csv'  
# Inseasopn Pilot Data 
Pilot_Run_Ins <- 'Daily Passage By Species.csv'
# Pilot Station Var  
Pilot_Var_Ins <- 'Daily Variance By Species.csv'
#-------------------------------------------------------------------------------
#  1.1: Set MSA data directory and file names 
#-------------------------------------------------------------------------------
source(file.path(fdr,'Yukon_Chum_MSA_STD.R'))  
source(file.path(fdr,'ggplot_theme.r'))  
library(ggplot2)    # Used for ggplot graphics 
#library(reshape2)
theme_set(theme_simple())
#theme_set(theme_adfg_bbc())
okabe.1 <- c("#000000","#E69F00","#56B4E9", "#009E73","#F0E442","#0072B2","#D55E00","#CC79A7" )
okabe <- c("#E69F00","#56B4E9", "#009E73","#F0E442","#0072B2","#D55E00","#CC79A7","#000000" )
options(ggplot2.discrete.color = okabe)
options(ggplot2.discrete.fill = list(okabe))
# Standard Output Stock figures 
ststockID <- c(4,7,8,10,11,19)
#	4 (P) Lower 
#	7 (P) UppKoy+Main
#	8 (P) Tanana Summer
#	10 (P) Tanana Fall  
#	11 (P) Border US
#	19 Total Canada (2004-present)
# ststocks needed to read as character
ststocks <- as.character(ststockID)
# Standard break date 
# '05/01','06/22','06/29','07/10','07/19','07/28','08/06','08/15','08/25','09/15'
stb2 <- function(year){
  stdates <- c('05/28/','06/22/','06/29/','07/10/','07/19/','07/28/','08/06/','08/15/','08/25/','09/15/')
  stdates <- paste0(stdates,year)
  stdates <- as.Date(stdates,'%m/%d/%Y')
  return(stdates) 
}
stbreak <- stb2(this.year)
# Pilot 

Pilot.total <- mlist[mlist$Strata==100,]
Pilot.summer <-mlist[mlist$Strata==101,]
Pilot.fall <- mlist[mlist$Strata==102,]
Pilot.fallinfall <- mlist[mlist$Strata==108,]

# Set legend name and order 
lgnames <- data.frame(t(stockID$GroupName))
names(lgnames) <- stockID$grpID
#-------------------------------------------------------------------------------
#  1.1: Set MSA data directory and file names 
#-------------------------------------------------------------------------------
#===============================================================================
#  2.0: Read summary data
#===============================================================================
#-------------------------------------------------------------------------------
#  2.1: Read Summer vs. Fall % data
#-------------------------------------------------------------------------------
# Read MSA minimum and max of the last year 
Pilot.d.min.max <- read.csv(file.path(wd_Sums,paste0('Pilot_d_min_max_',this.year-1,'.csv')),stringsAsFactors = FALSE)
# Read MSA Summer vs. Fall last yea
Pilot.hsft <- read.csv(file.path(wd_Sums,paste0('Pilot_sft_',this.year-1,'.csv')),stringsAsFactors = FALSE)
# Remove any years th 
Pilot.hsft <- Pilot.hsft[Pilot.hsft$Year < this.year,]
# Find the number of years in the data 
years <- unique(Pilot.hsft$Year)
years <- years[order(years)]
# number of years
ny <- length(years)

############################################################################
#  Add kniter and rmarkdown libraries
############################################################################
library(knitr)
library(rmarkdown)
library(kableExtra)
 add_legend <- function(...) {
   par(mar = c(0,0,4,0))
   plot(0, 0, type='n', bty='n', xaxt='n', yaxt='n',xlab='',ylab='')
   legend(...)
  }
```
# Pilot Station Passage 
```{r,fig.width=9, fig.height = 5,echo=FALSE,,warning=FALSE,dpi=400}
#-------------------------------------------------------------------------------
#  Plot Pilot Station Passage and the strata break 
#-------------------------------------------------------------------------------
  rstr.y <- rstr[rstr$Year==this.year,]
  xlims<-c(min(stbreak),max(stbreak))  
      ggplot() +
      geom_bar(data = Pilot, aes(x=Date,y=Run), stat='identity',color='grey')+
      scale_x_date(expand=c(0, 2),limits=as.Date(xlims),oob=oob_keep,date_labels="%b%d")+
      scale_y_continuous(expand=expansion(mult = c(0, .25)), limits=c(0, NA))+
      geom_vline(xintercept = c(rstr.y$Strata_Start_Date),color=4) + 
      geom_vline(xintercept = max(rstr.y$Strata_End_Date,na.rm=TRUE),color=2)


```
Figure 1.  Daily sonar counts attributed to chum salmon (bars) showing genetic sampling time frames (droplines), project operated near Pilot Station, Yukon Area, `r this.year`.

\newpage
# Stock proportion by sampling strata
```{r,fig.width=9, fig.height = 5,echo=FALSE,dpi=400}
#-------------------------------------------------------------------------------
#  Plot mean stock proportion by sampling strata 
#-------------------------------------------------------------------------------
# Pilot Station timing 
Pilot.stp <- Pilot.m[Pilot.m$Year == this.year,c('Year','Strata','Run', ststocks)]
Pilot.stp[,ststocks] <- 100*Pilot.stp[,ststocks] /Pilot.stp$Run
Pilot.stpl  <- reshapeWL(Pilot.stp[,c('Year','Strata',ststocks)], idvar = c('Year','Strata'), timevar = "group", v.names = "percent") 
Pilot.stpl$group <- factor(Pilot.stpl$group,levels = ststocks)
Pilot.stpl <- Pilot.stpl[order(Pilot.stpl$Year,Pilot.stpl$Strata),]
gname <- stockID[stockID$grpID %in%ststockID,c('GroupName')]      
names(gname) <- ststockID
nb <- length(unique(Pilot.stpl$Strata))
    ggplot(data = Pilot.stpl, aes(x=(Strata),y=percent,group=group))+
    geom_line(aes(colour=group))+geom_point(aes(shape=group,color=group))+ 
    scale_color_manual(values = okabe.1,labels = gname)+scale_shape_manual(values = c(1:6),labels = gname)+
    labs(x='Sampling Strata -standard dates',y='Stock Percent')+
    scale_x_continuous(expand=expansion(add = c(.25,.25)),breaks=seq(1,nb),labels=rstr[which(rstr$Year==this.year), 'Time_Frames'], limits=c(1, NA))+
        theme(axis.text.x = element_text(size = rel(0.75)))


```
Figure 2.  Mean proportion of chum salmon stock groups by sampling strata, Yukon Area, `r this.year`.

##  Stock proportion by strata (bar graph) 
```{r,fig.width=9, fig.height = 5,echo=FALSE,dpi=400}
#-------------------------------------------------------------------------------
#  Plot passage by stock and strata 
#-------------------------------------------------------------------------------
Pilot.stn <- Pilot.m[Pilot.m$Year == this.year,c('Year','Strata', c('4','7','8','11','19','10'))]
Pilot.stnl  <- reshapeWL(Pilot.stn, idvar = c('Year','Strata'), timevar = "group", v.names = "n")
Pilot.stnl$group <- factor(Pilot.stnl$group,levels = c('4','7','8','11','19','10'))
gname <- lgnames[c('4','7','8','11','19','10')]
        ggplot(data=Pilot.stnl,aes(x=as.factor(Strata),y=n,group=group))+ 
        geom_bar(stat = "identity", position = "dodge",aes(fill=group))+
        scale_fill_manual(values = okabe.1,labels = gname)+
        scale_x_discrete(labels=rstr[which(rstr$Year==this.year), 'Time_Frames'])+
        theme(axis.text.x = element_text(size = rel(0.75)))+
        labs(x = "Sampling Strata -standard dates", y = "Run size")

```
Figure 2.5  Mean proportion of chum salmon stock groups by sampling strata, Yukon Area, `r this.year`.

\newpage
# Historical mean stock proportion  
```{r,fig.width=9, fig.height = 5,echo=FALSE,dpi=400}
#-------------------------------------------------------------------------------
#  Plot stock proportion by Standard Strata
#-------------------------------------------------------------------------------
gname <- stockID[stockID$grpID %in%ststockID,c('GroupName')]      
names(gname) <- ststockID
df <- Pilot.d.min.max[Pilot.d.min.max$group %in% ststockID,]
df$group <- as.factor(df$group)
 ggplot(data = df, aes(x=as.factor(stbreak),y=Mean,group=group))+
      geom_line(aes(colour=group))+geom_point(aes(shape=group,colour=group))+                           scale_colour_manual(values = okabe.1,labels = gname)+scale_shape_manual(values = c(1:6),labels = gname)+
        scale_x_discrete(labels=stbl)+labs(x='Dates',y='Stock Percent')

```
Figure 3.  Mean proportion of chum salmon stock groups by standard sampling strata, Yukon Area, 2004-`r this.year-1`.


\newpage
# Standard Stock Inseason Proportion 
```{r,fig.width=9, fig.height = 9,echo=FALSE,dpi=400}
#-------------------------------------------------------------------------------
#  Plot mean stock prop overlapped by historical min-max
#-------------------------------------------------------------------------------
fig.stock.id <- c(4,7,8,10,11,19,16,3)
gname <- stockID[stockID$grpID %in%fig.stock.id,c('GroupName','grpID')]
gname$grpID <- as.character(gname$grpID)
new_order_indices <- match(as.character(fig.stock.id), gname$grpID)
name <- gname[new_order_indices,'GroupName']
df <- Pilot.d.min.max[Pilot.d.min.max$group %in% fig.stock.id,]
plt <- Pilot.sd[(Pilot.sd$group %in% fig.stock.id)&(Pilot.sd$Year==this.year),]
df <- merge(plt,df, by =c('stbreak','group'))
ggplot(data=df,aes(x=(stbreak)))+
  geom_ribbon(aes(ymin = Min, ymax = Max), fill = "gray", alpha = 0.5) +
 geom_line(aes(y=percent),colour=2)+
  scale_x_continuous(expand=expansion(add = c(.25, .25)),breaks=seq(1,9), labels=stbl, limits=c(1, NA))+
  facet_wrap( ~factor(group,labels=name,levels=as.character(fig.stock.id)),axes='all',axis.labels='margins',ncol=2)+
  labs(title="Stock Proportion thru Run",x="Dates",y='Stock Percent')+
  theme(axis.text.x = element_text(size = rel(0.8)))
```
Figure 4.  Minimum and maximum (2004-`r this.year-1`) and `r this.year` mean stock proportion by standard sampling strata, comparing the major chum salmon components, Yukon Area.

\newpage
# Summer vs. Fall:  All seasons
```{r,echo=FALSE}
# Summer vs. Fall data preparation: Inseason 
# Compbine historical and this year's data
   hsft <- rbind(Pilot.hsft,Pilot.sft)
# Get length
   tyears <- c(years,this.year)
   tny <- length(tyears)
#   df<- melt(hsft[,c(1,2,4,5)],id.vars=c('Year','stbreak'), 
#                       variable.name='SF', value.name='percent')
   df <-reshapeWL(hsft[,c(1,2,4,5)],idvar=c('Year','stbreak'),timevar='SF', v.names='percent')
#   df<- reshape(hsft[,c(1,2,4,5)], idvar =c('Year','stbreak'),
#                varying =3:4,
#                v.names = 'percent',
#                timevar='SF',
#                times=names(hsft[,c(1,2,4,5)])[3:4],
#                direction = 'long'
#                )
```


```{r,fig.width=9, fig.height = 9,echo=FALSE,dpi=400}
#-------------------------------------------------------------------------------
# Plot Summer vs. Fall cross over all years and strata
#-------------------------------------------------------------------------------
  ggplot(data=df,aes(x=as.factor(stbreak),y=percent,group=SF)) + theme_simple() + 
      geom_line(aes(color=SF ))+
      geom_point(aes(color=SF),size=2)+
      facet_wrap( ~Year,axes='all',axis.labels='margins',ncol=5) +
      scale_x_discrete(labels=stbl,guide = guide_axis(check.overlap = TRUE)) + 
	  ylim(0, 100)+
      theme(axis.text.x = element_text(size=7))+
      labs(title = "Summer vs. Fall (All Strata)")+  xlab("Dates")

```
Figure 5.  Crossover of summer and fall chum salmon based on genetic stock analysis (standard sampling strata), Yukon Area, 1999-2002 using allozymes and 2004-`r this.year` using microsatellites.

\newpage
# Summer vs. Fall:  During the transition periods



```{r,fig.width=9, fig.height = 9,echo=FALSE,warning=FALSE,dpi=400}

#-------------------------------------------------------------------------------
# Plot Summer vs. Fall cross over all years and strata
#-------------------------------------------------------------------------------
  ggplot(data=df,aes(x=as.factor(stbreak),y=percent,group=SF))+ 
      geom_line(aes(color=SF ))+
      geom_point(aes(color=SF),size=2)+
      facet_wrap( ~Year,axes='all',axis.labels='margins',ncol=5) +
      scale_x_discrete(labels=stbl,limit=factor(4:6),guide = guide_axis(check.overlap = TRUE)) + 
	  ylim(0, 100)+
      theme(axis.text.x = element_text(size=7))+
      labs(title = "Summer vs. Fall")+  xlab("Dates")

```
Figure 6.  Crossover of summer and fall chum salmon (3 periods) based on genetic stock analysis (standard sampling strata), Yukon Area, 1999-2002 using allozymes and 2004-`r this.year` using microsatellites.

\newpage
# Fall Stock Inseason Proportion 
```{r,fig.width=9, fig.height = 9,echo=FALSE,dpi=400}
if(dim(Pilot.fall)[1]>0){
temp <- Pilot.fall[Pilot.fall$grpID %in% c(4,7,8,10,11,13,16),]
temp$pct <- with(temp, paste0(round(100*p),'%'))
temp$lab.ypos = with(temp, cumsum(p) +0.2)
ggplot(temp,aes(x='',y=p,fill=GroupName))+
geom_col(color='black')+
geom_text(aes(x=1.6,label=pct),position=position_stack(vjust=0.5))+
coord_polar("y")+
labs(title="Stock Proportion (July 19 to End of Season)",x='',y='')+
  theme(axis.line = element_blank(),
       axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        panel.grid = element_blank())
}
```
Figure 7. Contributions of chum salmon based on genetic analysis during the fall season (July 19 to end of season), sampled at the mainstem sonar operated near Pilot Station, Yukon Area, `r this.year`.

```{r,fig.width=9, fig.height = 9,echo=FALSE,dpi=400}
if(dim(Pilot.fallinfall)[1]>0){
  temp <- Pilot.fallinfall[Pilot.fallinfall$grpID %in% c(10,11,19),]
temp$pct <- with(temp, paste0(round(100*p),'%'))
ggplot(temp,aes(x='',y=p,fill=GroupName))+
#geom_bar(stat = "identity", color = "white") +  
geom_col(color='black')+
geom_text(aes(x=1.6, label=pct),position=position_stack(vjust=0.5))+
coord_polar("y")+
labs(title="Stock Proportion (July 19 to End of Season)",x='',y='')+
  theme(axis.line = element_blank(),
       axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        panel.grid = element_blank())
}
```
Figure 8. Contributions of Fall chum salmon based on genetic analysis during the fall season (July 19 to end of season), sampled at the mainstem sonar operated near Pilot Station, Yukon Area, `r this.year`.


\newpage
# Tables
```{r,echo=FALSE}
table <- mlist[which(mlist$Strata<10 & mlist$SortID<20),]
```

**Table 1. Genetic proportions of chum salmon stock groupings from samples collected from mainstem Yukon River (Pilot Station) sonar test fishery `r this.year`.**
```{r,echo=FALSE}
table$p <- table$p*100
#Prop <- dcast(table,SortID+GroupName~Strata,value.var='p')
Prop <- reshapeLW(table,idvar=c('SortID','GroupName'),timevar='Strata',v.names='p')
s.names <- with(rstr,paste(paste('Strata',Strata),Time_Frames,paste('n=',Sample_Size),sep='<br/>'))
t.names <-c('Stock',s.names)
kable(Prop[,-1],digits=1,format = "html",col.names=t.names,format.args = list(big.mark = ",",scientific = F),escape=FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

\newpage
**Table 2. Genetic estimates of chum salmon passage by stock groups applied to mainstem Yukon River (Pilot Station) sonar counts `r this.year`.**
```{r,echo=FALSE}
n <- reshapeLW(table,idvar=c('SortID','GroupName'),timevar='Strata',v.names='mean')

#n <- dcast(table,SortID+GroupName~Strata,value.var='mean')
total <- rowSums(n[,-c(1,2)])
n <- cbind(n,total)
s.names <- with(rstr.y,paste(paste('Strata',Strata),Time_Frames,paste('n=',Sample_Size),sep='<br/>'))
t.names <-c('Stock',s.names,'Total')
kable(n[,-1],digits=0,format = "html",, booktabs = T,longtable=T,col.names=t.names,format.args = list(big.mark = ",",scientific = F),escape=FALSE) %>%
  kable_styling(bootstrap_options = c("striped"))
```



