---
title: "Yukon River Fall Chum Salmon Mixed Stock Analysis"
output:
#  html_document:
#    toc: true
#    theme: united
  word_document:
    reference_docx: defalult-style_01.docx
    toc: false
#   This function will save output file with date. 
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_file = paste0(
        xfun::sans_ext(input), '-', Sys.Date(), '.docx'
      ),
      envir = globalenv()
    )
  })
---


```{r get_data, message=FALSE,echo=FALSE,error=FALSE,warning=FALSE}
#-------------------------------------------------------------------------------
# Setup file directories 
#-------------------------------------------------------------------------------
# Clear up existing files 
rm(list = ls(all.names = TRUE))
#-------------------------------------------------------------------------------
# Standard 
#-------------------------------------------------------------------------------
# Main <- 'C:/Projects/Yukon_River/Fall_Chum/MSA/' 
# fdr <- paste0(Main, 'R_functions/')  # R functions
#-------------------------------------------------------------------------------
# R projects 
#-------------------------------------------------------------------------------
fdr <- './R_functions/'
#===============================================================================
#  1.0: Run MSA
#===============================================================================
PostSeason <- FALSE 
# Set year 
this.year <- 2022
#-------------------------------------------------------------------------------
#  1.1: Set MSA data directory and file names 
#-------------------------------------------------------------------------------
source(paste0(fdr,'Yukon_Chum_MSA_RUN.R'))  
stbreak <- stb(this.year)
Pilot.total <- mlist[mlist$Strata==100,]
Pilot.summer <-mlist[mlist$Strata==101,]
Pilot.fall <- mlist[mlist$Strata==102,]
Pilot.fallinfall <- mlist[mlist$Strata==108,]

# Set legend name and order 
lgnames <- data.frame(t(stockID$GroupName))
names(lgnames) <- stockID$grpID
#-------------------------------------------------------------------------------
#  1.1: Set MSA data directory and file names 
#-------------------------------------------------------------------------------
#===============================================================================
#  2.0: Read summary data
#===============================================================================
#-------------------------------------------------------------------------------
#  2.1: Read Summer vs. Fall % data
#-------------------------------------------------------------------------------
# Read MSA Strata data
#Pilot.d.min.max <- read.csv(paste0(wd_Sum,'Pilot_d_min_max.csv'),stringsAsFactors = FALSE)
# Use Last years min max 
Pilot.d.min.max <- read.csv(paste0(wd_Sum,'Pilot_d_min_max_',this.year-1,'.csv'),stringsAsFactors = FALSE)

# Read MSA Strata data
Pilot.hsft <- read.csv(paste0(wd_Sum,'Pilot_sft.csv'),stringsAsFactors = FALSE)
# Find the number of years in the data 
years <- unique(Pilot.hsft$Year)
years <- years[order(years)]
# number of years
ny <- length(years)

############################################################################
#  Add kniter and rmarkdown libraries
############################################################################
library(knitr)
library(rmarkdown)
 add_legend <- function(...) {
   par(mar = c(0,0,4,0))
   plot(0, 0, type='n', bty='n', xaxt='n', yaxt='n',xlab='',ylab='')
   legend(...)
  }
```

```{r,fig.width=9, fig.height = 5,echo=FALSE,dpi=400}
# Pilot Station timing 
par(mfrow=c(1,1),mar = c(2,2,2,2),oma = c(3,3,3,3),yaxs='i',bty='l',las=1)
  rstr.y <- rstr[rstr$Year==this.year,]
  xlims<-c(min(stbreak),max(stbreak))
  plot(Run~Date, type='h',lwd=4,col='gray',data=Pilot,xlim=xlims,xaxt='n')
  axis.Date(1, at = stbreak,format= "%b%d",cex=0.6)
  abline(v=c(rstr.y$Strata_Start_Date),col=4,lwd=2)
mtext(paste("Sampling Strata"), side = 3, line = 0, outer = TRUE,cex=1.5)
mtext('Number of Salmon', side = 2, line = 1.5, las=0, outer = TRUE,cex=1.5)
mtext("Date", side = 1, line = 1, outer = TRUE,cex=1.5)
```
Figure 1.  Daily sonar counts attributed to chum salmon (bars) showing genetic sampling time frames (droplines), project operated near Pilot Station, Yukon Area, `r this.year`.

```{r,fig.width=9, fig.height = 5,echo=FALSE,dpi=400}
#-------------------------------------------------------------------------------
#  Plot mean stock proportion by sampling strata 
#-------------------------------------------------------------------------------
# Pilot Station timing 
Pilot.stp <- Pilot.m[,c('Year','Strata','Run', ststocks)]
Pilot.stp[,ststocks] <- 100*Pilot.stp[,ststocks] /Pilot.stp$Run
Pilot.stpl <- melt(Pilot.stp[,c('Year','Strata',ststocks)], 
                   id.vars = c('Year','Strata'), variable.name = "group", value.name = "percent") 
Pilot.stpl <- Pilot.stpl[order(Pilot.stpl$Year,Pilot.stpl$Strata),]
gname <- stockID[stockID$grpID %in%ststockID,c('GroupName')]      
names(gname) <- ststockID
# Base plot 
layout(matrix(1:2, ncol=2), widths=c(3,1))
par(mar=c(4, 4, 4, 0),yaxs='i',bty='l',las=1) 
temp1 <- Pilot.stpl[Pilot.stpl$group==ststockID[1],]
plot(order(temp1$Strata),type='n', xlim=c(1,7),ylim=c(0,100), ylab='Stock Percent',xlab='Sample Strata Number')
for (i in 1:6){
  lines(percent~Strata, type ='o',lwd=2,col=i,pch=i,data=Pilot.stpl[Pilot.stpl$group==ststockID[i],])
}
title(main = this.year)
add_legend('topleft',legend = gname,col = c(1:6), pch=c(1:6),lty=1,lwd=2,bty = 'n')
mtext('Stock Percent', side = 2, line = 1,las=0, outer = TRUE)
mtext("Sampling Strata", side = 1, line = 1, outer = TRUE)

```
Figure 2.  Mean proportion of chum salmon stock groups by sampling strata, Yukon Area, `r this.year`.

```{r,fig.width=9, fig.height = 5,echo=FALSE,dpi=400}
#Pilot.stn <- Pilot.m[,c('Year','Strata','Run', c('4','8','11','19','10'))]
#gname <- lgnames[c('4','8','11','19','10')]      

#par(mfrow=c(1,1),mar=c(4.1, 6.1, 4.1, 4.1),yaxs='i',bty='l',las=1) 
#barplot(t(Pilot.stn[,-c(1:3)]),beside=TRUE,col=c(2:6),
#        names.arg = rstr[which(rstr$Year==this.year), 'Time_Frames']
#        )
#title(main = this.year)
#legend('topright',legend = gname, fill = c(2:6),bty = 'n')
#mtext('Run size', side = 2, line = 4,las=0)
#mtext("Sampling Strata", side = 1, line = 2)
```



```{r,fig.width=9, fig.height = 5,echo=FALSE,dpi=400}
#-------------------------------------------------------------------------------
#  Plot mean stock proportion by Standard Strata
#-------------------------------------------------------------------------------
gname <- stockID[stockID$grpID %in%ststockID,c('GroupName')]      
names(gname) <- ststockID
layout(matrix(1:2, ncol=2), widths=c(3,1))
par(mar = c(4,4,4,0),yaxs='i',bty='l',las=1)
temp1 <- with(Pilot.d.min.max, Pilot.d.min.max[group ==ststockID[1],])
plot(order(temp1$stbreak),type='n', xlim=c(1,9),ylim=c(0,100), ylab='',xlab='',
     yaxt='n',xaxt='n')
axis(2, seq(0,100,20),las=2, font=2 )
axis(1, seq(1,9,1), labels = stbl,tick=1)
for(i in 1:6){
  temp <- with(Pilot.d.min.max, Pilot.d.min.max[group ==ststockID[i],])  
  temp <- temp[order(temp$stbreak),]
  with(temp, lines(stbreak,Mean, type='o',lwd=2,col=i,pch=i))
}
txt <- c(gname)
add_legend('topleft',legend=txt,col=c(1:6),pch=c(1:6),lty=1,lwd=2,bty='n')
mtext(paste(" "), side = 3, line = 0, outer = TRUE)
mtext('Stock Percent', side = 2, line = 1,las=0, outer = TRUE)
mtext("Dates", side = 1, line = 1, outer = TRUE)

```
Figure 3.  Mean proportion of chum salmon stock groups by standard sampling strata, Yukon Area, 2004-`r this.year-1`.
```{r,fig.width=9, fig.height = 9,echo=FALSE,dpi=400}
par(mfrow=c(4,2),mar = c(2,2,2,2),oma = c(3,3,3,3),yaxs='i',bty='l')
fig.stock.id <- c(4,7,8,11,10,19,16,3)
for(j in 1:8){
  temp1 <- with(Pilot.d.min.max, Pilot.d.min.max[group ==fig.stock.id[j],])
  temp1 <- temp1[order(temp1$stbreak),]
  plot(Mean~stbreak,data=temp1, type='n',xlim=c(1,9),ylim=c(0,100), 
       yaxt='n',xaxt='n',main=unique(temp1$GroupName))
  axis(2, seq(0,100,20),las=2, label=FALSE)
  if(j %in% c(1,3,5,7)) {axis(2, seq(0,100,20),las=2, font=2)}
  axis(1,seq(1,9,1), labels = FALSE,tick=1)
  if(j %in% c(7:8)) {axis(1, seq(1,9,1), labels = stbl,tick=1)}
  with(temp1,polygon(c(stbreak,rev(stbreak)),c(Min,rev(Max)),col=tcol('gray',0),border=NA))
  lines(percent~stbreak,lwd=2,col=2, data=Pilot.sd[Pilot.sd$ group ==fig.stock.id[j],])
  }

mtext(paste("Stock Proportion thru Run"), side = 3, line = 0, outer = TRUE)
mtext('Stock Percent', side = 2, line = 1, outer = TRUE)
mtext("Dates", side = 1, line = 1, outer = TRUE)

```
Figure 4.  Minimum and maximum (2004-`r this.year-1`) and `r this.year` mean stock proportion by standard sampling strata, comparing the major chum salmon components, Yukon Area.
```{r,fig.width=9, fig.height = 9,echo=FALSE,dpi=400}
  par(mfrow=c(5,5),mar = c(2,2,2,2),oma = c(3,3,3,3),yaxs='i',bty='l') 
  for(i in 1:ny){
    temp <- with(Pilot.hsft, Pilot.hsft[Year==years[i],])
    plot(Summer~stbreak, type ='o',col=4, xlim=c(1,9),ylim=c(0,100), 
         yaxt='n',xaxt='n',lwd = 2, data=temp,main=years[i])
    lines(Fall~stbreak,type ='o',col=2,lwd = 2, data=temp)
    axis(2, seq(0,100,20),las=2, labels=NA)
    if (years[i] %in% c(1999,2005, 2010,2015, 2020)) axis(2, seq(0,100,20),las=2, font=2)
    axis(1, seq(1,9,1),labels = NA,cex.axis = 0.9)
    if (years[i] > 2017) axis(1, seq(1,9,1), labels = stbl,cex.axis = 0.9)
  }
# This year 
 plot(Summer~stbreak, type ='o',col=4, xlim=c(1,9),ylim=c(0,100), 
     yaxt='n',xaxt='n',lwd = 2, data=Pilot.sft,main=this.year)
 lines(Fall~stbreak,type ='o',col=2,lwd = 2, data=Pilot.sft)
 axis(2, seq(0,100,20),las=2, font=2)
 axis(1, seq(1,9,1), labels = stbl,cex.axis = 0.9)
 
  mtext(paste("Summer vs. Fall (All Strata)"), side = 3, line = 0, outer = TRUE,cex=1.5)
  mtext('Stock Percent', side = 2, line = 1, outer = TRUE,cex=1.5)
  mtext("Dates ", side = 1, line = 1, outer = TRUE,cex=1.5)
```
Figure 5.  Crossover of summer and fall chum salmon based on genetic stock analysis (standard sampling strata), Yukon Area, 1999-2002 using allozymes and 2004-`r this.year` using microsatellites.
```{r,fig.width=9, fig.height = 9,echo=FALSE,dpi=400}
  par(mfrow=c(5,5),mar = c(2,2,2,2),oma = c(3,3,3,3),yaxs='i',bty='l') 
    for(i in 1:ny){
    temp <- with(Pilot.hsft, Pilot.hsft[Year==years[i],])
    plot(Summer~stbreak, type ='o',col=4, xlim=c(4,6),ylim=c(0,100), 
         yaxt='n',xaxt='n',lwd = 2, data=temp,main=years[i])
    lines(Fall~stbreak,type ='o',col=2,lwd = 2, data=temp)
    axis(2, seq(0,100,20),las=2, labels=NA)
    if (years[i] %in% c(1999,2005, 2010,2015, 2020)) axis(2, seq(0,100,20),las=2, font=2)
    axis(1, seq(1,9,1),labels = NA,cex.axis = 0.9)
    if (years[i] > 2017) axis(1, seq(1,9,1), labels = stbl,cex.axis = 0.9)
    }
# This year 
  plot(Summer~stbreak, type ='o',col=4, xlim=c(4,6),ylim=c(0,100), 
       yaxt='n',xaxt='n',lwd = 2, data=Pilot.sft,main=this.year)
  lines(Fall~stbreak,type ='o',col=2,lwd = 2, data=Pilot.sft)
  axis(2, seq(0,100,20),las=2, font=2)
  axis(1, seq(1,9,1), labels = stbl,cex.axis = 0.9)
  
  mtext(paste("Summer vs. Fall"), side = 3, line = 0, outer = TRUE,cex=1.5)
  mtext('Stock Percent', side = 2, line = 1, las=0, outer = TRUE,cex=1.5)
  mtext("Dates", side = 1, line = 1, outer = TRUE,cex=1.5)

```
Figure 6.  Crossover of summer and fall chum salmon (3 periods) based on genetic stock analysis (standard sampling strata), Yukon Area, 1999-`r this.year` using allozymes and 2004-`r this.year` using microsatellites.
```{r,fig.width=9, fig.height = 9,echo=FALSE,dpi=400}
if(dim(Pilot.fall)[1]>0){
  temp <- Pilot.fall[Pilot.fall$grpID %in% c(4,7,8,10,11,13,16),]
temp$pct <- with(temp, paste0(round(100*p),'%'))
par(mfrow=c(1,1),mar = c(4,4,4,7),oma = c(3,3,3,3))
pie(temp$p, labels = paste(temp$GroupName,temp$pct),col=c(2:8),main="Stock Proportion (July 19 to End of Season)")
#par(new=TRUE)
#pie(temp$p,density=10, labels='',angle=c(20,90,30,10,40,0))
#pie(temp$p, labels = paste(temp$GroupName,temp$pct),col=gray.colors(6),main="Stock Proportion (July 19 to End of Season)")
}
```
Figure 7. Contributions of chum salmon based on genetic analysis during the fall season (July 19 to end of season), sampled at the mainstem sonar operated near Pilot Station, Yukon Area, `r this.year`.
```{r,fig.width=9, fig.height = 9,echo=FALSE,dpi=400}
if(dim(Pilot.fallinfall)[1]>0){
  temp <- Pilot.fallinfall[Pilot.fallinfall$grpID %in% c(10,11,19),]
temp$pct <- with(temp, paste0(round(100*p),'%'))
par(mfrow=c(1,1),mar = c(4,4,4,7),oma = c(3,3,3,3))
pie(temp$p, labels = paste(temp$GroupName,temp$pct),col=c(2:8),main="Stock Proportion (July 19 to End of Season)")
#par(new=TRUE)
#pie(temp$p,density=10, labels='',angle=c(20,90,30,10,40,0))
#pie(temp$p, labels = paste(temp$GroupName,temp$pct),col=gray.colors(6),main="Stock Proportion (July 19 to End of Season)")
}
```
Figure 8. Contributions of Fall chum salmon based on genetic analysis during the fall season (July 19 to end of season), sampled at the mainstem sonar operated near Pilot Station, Yukon Area, `r this.year`.